---
title: "amcat for document storage"
bibliography: references.bib
---

::: {.callout-note}
The minimum modules you need to use this module:
:::

## Fill your database

::: {.callout-important}
# Will change soon

Currently, there is no way to add data through the web interface.
Rather, you can add new datasets through calls to the amcat API.
:::

You can upload document to the amcat server by using our [`R` package](#manage-storage-using-r), [`Python` package](#manage-storage-using-python) or calling the [API directly](#manage-storage-using-api-calls).
Of course, you can use the calls in the [API section]() and write an API wrapper in another language of your choice.
Let us know about it and we will promote your package here.

### Manage storage using `R`

```{r eval=FALSE}
remotes::install_github("ccs-amsterdam/amcat4r")
```

```{r eval=FALSE}
library(amcat4r)
login(host = "http://opted.amcat.nl", username = "admin")
#> No encoding supplied: defaulting to UTF-8.
```

### Manage storage using `Python`

::: {.callout-important}
# Coming soon...
:::

### Manage storage using API calls

::: {.callout-important}
# Coming soon...
:::
